Current State of Knowledge Representation Systems for Robotics

### 2011-11-25 krs-survey.tex
Filled section on monotonicity

The family of \emph{description logics}~\cite{Baader2008} also play an
important role. It is a subset of the first-order logic, with some extensions
in second-order logic. Description logics are notable because most of them are
known to be decidable. In description logic, axioms are build from
\emph{concepts}, \emph{roles} (that are unary or binary predicates) and
\emph{individuals}. \emph{Modal logics}, that allow for statement qualification
(like \emph{possibility} or \emph{necessity}) have been shown to be closely
related to description logics.

@@

One last class of logics that is of particular relevance for robotic
applications is the \emph{probabilistic logics} or \emph{bayesian logics}.
These logics provide a formal framework to reason on propositions whose truth
or falsity is uncertain.

@@

\paragraph{(non) monotonic reasoning}

@@

\paragraph{General knowledge + exception to this knowledge (blue sky/white sky)}

>>>>

The family of \emph{description logics}~\cite{Baader2008} also play an
important role. It is a subset of the first-order logic, with some extensions
in second-order logic. Description logics are notable because most of them are
known to be decidable. In description logic, axioms are build from
\emph{concepts}, \emph{roles} (that are unary or binary predicates) and
\emph{individuals}. The W3C OWL-DL standard is a widely-used language to describe
domain with the description logic.

\emph{Modal logics}, that allow for statement qualification
like \emph{possibility} or \emph{necessity}, have been shown to be closely
related to description logics.

@@

One last class of logics that is of particular relevance for robotic
applications is the \emph{probabilistic logics} or \emph{bayesian logics}.
These logics provide a formal framework to reason on propositions whose truth
or falsity is uncertain. We elaborate below on the representation of uncertainty.

@@

\paragraph{(Non) Monotonic Reasoning}

\emph{Monotonic reasoning} means that addition of new assertions to a knowledge base
can only extend the set of assertions that can be inferred, while a
\emph{non-monotonic} reasoning scheme may lead to retraction of facts.
McCarthy coined a famous example to illustrate the need of non-monotonic reasoning:

\begin{quotation}
Consider putting an axiom in a common sense database asserting that birds can
fly. Clearly the axiom must be qualified in some way since penguins, dead birds
and birds whose feet are encased in concrete can't fly. A careful construction
of the axiom might succeed in including the exceptions of penguins and dead
birds, but clearly we can think up as many additional exceptions like birds
with their feet encased in concrete as we like. Formalized nonmonotonic
reasoning provides a way of saying that a bird can fly unless there
is an abnormal circumstance and reasoning that only the abnormal circumstances
whose existence follows from the facts being taken into account will be
considered.
\end{quotation}

\emph{Default logic} is one of the formal logic that account for representing
general truth and exceptions to it. However, due to computational complexity of
these model (most of inferences in default logic are known to be $NP$-complete
problem), classical logics and most of the existing reasoners do not allow
non-monotonic reasoning. For instance, the SWRL rule language, usually
associated to the OWL-DL ontology language, do not allow non-monotonic
reasoning.

\fxfatal{Make clear 'who does not allow non-monotonic-reasoning': logics? rule
languages? reasoner?}

One important exception if the \emph{Negation as failure} inference rule, as
implemented by {\sc Prolog} for instance, that allows for non-monotonicity, but
only \emph{within the closed world assumption}.

\fxfatal{Give here an example of non-monotonic reasoning with Prolog}

A monotonic system does not theoritically allow for knowledge retractation,
which is an important issue in the robotic context where the world model is
likely to be often altered.  However it is a practical issue only if the
reasoning process is \emph{continuous} during the whole robot's activity
lifespan. It is often possible to stop the reasoner, alter the knowledge, and
restart the inference process on a new domain.

@@
